Constructing the transition graphs of interacting hysterons

### 2022-06-28 Paper_draft.tex
Moved pieces about exchange symmetry & Garden of Eden states to model section

The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between states. For a system of $N$ hysterons, there are $2^N$ possible states. In particular there are two saturated states, where either all $s_i=0$ or all $s_i=1$. Each state $S$ has a single up and down transition, except for the two saturated states, which only have an up and a down transition respectively.  Therefore, a transition graph for a collection of $N$ hysterons consists of a maximum of $2^N$ states and $2(2^N-1)$ transitions. It can occur that not all of the $2^N$ states are included in the transition graph, because it is possible for a state to not be reachable, or to only be reachable as an unstable intermediate state of an avalanche. We discuss unreachable states in more detail in Section \ref{ssec:candidate_graphs}.
\subsection{Evaluation of switching fields}

@@

In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs. We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\\

@@

Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition. For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}). We will now make two considerations that reduce the number of candidate graphs, namely exchange symmetry and garden-of-Eden states. 

@@

To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state. For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011. Since there are $N!$ permutations of the order of $N$ hysterons, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$. Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.

>>>>

The possible responses of a collection of $N$ hysterons to driving are captured by a state transition graph, which consists of all stable states $S$ and all transitions between states. For a system of $N$ hysterons, there are $2^N$ possible states. In particular there are two saturated states, where either all $s_i=0$ or all $s_i=1$. Each state $S$ has a single up and down transition, except for the two saturated states, which only have an up and a down transition respectively.  Therefore, a transition graph for a collection of $N$ hysterons consists of a maximum of $2^N$ states and $2(2^N-1)$ transitions. It can occur that not all of the $2^N$ states are included in the transition graph, because it is possible for a state to not be reachable, or to only be reachable as an unstable intermediate state of an avalanche. We now make two considerations that affect the number of distinct graphs, namely exchange symmetry and Garden-of-Eden states.
\subsection{Uniqueness considerations}
We now describe two considerations that decrease the number of unique transition graphs, namely the 
To account for exchange symmetry, we fix the order in which hysterons 1, 2, ..., N flip up when increasing the external field from the ground state. For example, for $N=3$, we have that hysteron 3 flips up first from the state 000, hysteron 2 flips up first from 001, and trivially hysteron 1 flips up first from 011. Since there are $N!$ permutations of the order of $N$ up switching fields, accounting for exchange symmetry decreases the number of candidate graphs by a factor $N!$. Thus, for $N=2$, the number of candidate graphs is reduced by a factor 2 from 2916 to 1458.
\subsection{Ordering of switching fields}

@@

In addition to being an efficient method for conclusively finding the possible graphs, the method of candidate graphs also allows us to consider rational design of graphs. We can use the candidate graph method to directly consider the possibility of the interesting behaviours that have been observed previously, such as multiperiodic cycles and long transients, for a  given number of hysterons.\

@@

Naively, one can construct all possible transition graphs by finding the possible transition paths for each individual transition. For example, for $N=2$ one finds $3^4\times 6^2 = 2916$ graphs (Fig.\ref{fig:transition_paths_N2}).\\

@@
